Local Type Inference for Polarised System F with Existentials

### 2024-05-07 oopsla24/tex/03-declarative-system.tex
edit (misc)

\paragraph{Invariant Shifts}
As mentioned above, an important restriction that we put on the subtyping system
is that subtyping of shifted types requires their equivalence, as shown in
\ruleref{\ottdruleDOneShiftDLabel} and \ruleref{\ottdruleDOneShiftULabel}. The
reason for this is that if both of these rules were relaxed to the covariant
form, the subtyping relation would become equivalent to the standard subtyping
of \systemf, which is undecidable \cite{tiuryn-urzczyn-96}. However, after
certain changes \ruleref{\ottdruleDOneShiftULabel} can be relaxed to the
covariant form, thereby increasing the expressiveness of the system. These
changes are discussed in \cref{sec:weakening-invariant}.

>>>>

\paragraph{Invariant Shifts}
As mentioned above, an important restriction that we put on the subtyping system
is that subtyping of shifted types requires their equivalence, as shown in
\ruleref{\ottdruleDOneShiftDLabel} and \ruleref{\ottdruleDOneShiftULabel}. The
reason for this is that if both of these rules were relaxed to the covariant
form, the subtyping relation would become equivalent to the standard subtyping
of \systemf, which is undecidable \cite{tiuryn-urzczyn-96}. However, it is
suggested after certain changes \ruleref{\ottdruleDOneShiftULabel} can be
relaxed to the covariant form, thereby increasing the expressiveness of the
system. These changes are discussed in \cref{sec:weakening-invariant}.

### 2024-05-07 oopsla24/tex/04-algorithm.tex
edit (misc)

@@

Substitution $[[uσ]]$ satisfies a constraint \emph{set}
if $[[Θ ⊢ SC]]$ and \emph{each entry} of $[[SC]]$ is satisfied by $[[uσ]]$.

>>>>

\paragraph{Equivalent Substitutions}
In the proofs of the algorithm correctness, 
we often state or require that two substitutions are equivalent
on a given set of algorithmic variables.
We denote it as $[[Θ ⊢ uσ' ≈ uσ : Ξ]]$ meaning that
for each $[[α̂±]]$ in $[[Ξ]]$, substitutions $[[uσ]]$ and $[[uσ']]$
map $[[α̂±]]$ to types equivalent in the corresponding context:
$[[ Θ(α̂±) ⊢ [uσ']α̂± ≈ [uσ]α̂± ]]$.

@@

Substitution $[[uσ]]$ satisfies a constraint \emph{set} $[[SC]]$
if $[[Θ ⊢ SC]]$ and \emph{each entry} of $[[SC]]$ is satisfied by $[[uσ]]$.
